This file contains code to complete A\-D\-L\-C task specified in the A\-U\-V\-S\-I rules\-:

7.\-3. A\-U\-T\-O\-M\-A\-T\-I\-C D\-E\-T\-E\-C\-T\-I\-O\-N, L\-O\-C\-A\-L\-I\-Z\-A\-T\-I\-O\-N, A\-N\-D C\-L\-A\-S\-S\-I\-F\-I\-C\-A\-T\-I\-O\-N (A\-D\-L\-C) T\-A\-S\-K (S\-E\-C\-O\-N\-D\-A\-R\-Y) Table 4\-:  \-A\-D\-L\-C Parameters Parameter Threshold Objective Automatic Localization (each target, standard, and Q\-R\-C) n/a Identify target position within 150 ft. Automatic Classification (each standard target) n/a Identify at least three of five target characteristics. Automatic Classification (each Q\-R\-C target) n/a Decode the message. False Alarm Rate (F\-A\-R) on Classification n/a Demonstrate $<$50\% F\-A\-R.

7.\-3.\-1. Teams shall develop an algorithm which performs automated detection of potential targets and cues the imagery judge.\-  \-The algorithm shall localize the detected targets and automatically determine the target characteristics.

7.\-3.\-2. Credit will be given for each target automatically detected \& cued, up to six targets.

7.\-3.\-3. A\-D\-L\-C may be performed by any combination of airborne or ground‐based processing.

7.\-3.\-4. Teams shall make their A\-D\-L\-C process very clear to the imagery judge prior to aircraft takeoff. 7.\-3.\-4.\-1. If a judge is unclear about or suspects manual assistance to the A\-D\-L\-C process, the team shall not receive A\-D\-L\-C task points.

7.\-3.\-5. Demonstrating an A\-D\-L\-C target 7.\-3.\-5.\-1. A\-L\-L automatic detections shall be clearly shown to the imagery judge without human interaction (e.\-g. a pop‐up window).    7.\-3.\-5.\-2. The first six detections shown shall be considered a team’s entry for the A\-D\-L\-C task.\-  \-These detections shall be turned into the judges by filling out a single dedicated target information sheet, given in Appendix E. This target information sheet shall be marked clearly with “\-Automatic Detections” and handed in separate from other imagery sheets. or provided electronically in accordance with Appendix D, and clearly marked in tab 11 as “\-Auto Detection

7.\-3.\-6. False Alarm Rate 7.\-3.\-6.\-1. If a listed target fails to meet the objective for classification, the target will be considered a false detection.\-  \-The number of incorrect A\-D\-L\-C targets reported will be divided by the total number of A\-D\-L\-C targets reported to determine false alarm rate. 7.\-3.\-6.\-2. Each detection/target is counted once.\-  \-If the false alarm rate exceeds the objective limit, no credit will be given for the A\-D\-L\-C task 